---
title: "Testing for Lab 1"
author: "Cale Bible"
date: "r Sys.date()"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

These are the tasks for the first lab.

## Task 1

```{r, include=TRUE}
setwd("C:/Users/golfe/Desktop/Applied Statistical Methods/LAB1")
getwd()
list.files()
```
## Task 2

Reading in the data into ddt.
```{r}
ddt <- read.csv("Dataxls/Dataxls/DDT.csv")
head(ddt)
```

## Task 3
- Using class() function, we can conclude that SPECIES and RIVER classes are quantitative data, since they have character values.
```{r}
class(ddt$SPECIES)
class(ddt$RIVER)
```
- Likewise, we can conclude the quantitative variables of the data frame are: MILE, LENGTH, and WEIGHT
```{r}
class(ddt$MILE)
class(ddt$LENGTH)
class(ddt$WEIGHT)
```
Next, finding observations with SPECIES, LMBASS and WEIGHT bigger than 800gms. We set species equal to "LMBASS" and WEIGHT>800.
```{r}
#FIXME
sbst=with(ddt,table(SPECIES=="LMBASS", WEIGHT>800))
```

Next, finding observations where the RIVER is SCM and DDT bigger than 4.0. We set RIVER equal to "SCM" and DDT>4.0.
```{r}
#FIXME
sbst=with(ddt,table(SPECIES=="LMBASS", WEIGHT>800))
```