---
title: "Testing for Lab 1"
author: "Cale Bible"
date: "r Sys.date()"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

These are the tasks for the first lab.

## Task 1

```{r, include=TRUE}
setwd("C:/Users/golfe/Desktop/Applied Statistical Methods/LAB1")
getwd()
list.files()
```
## Task 2

Reading in the data into ddt.
```{r}
ddt <- read.csv("Dataxls/Dataxls/DDT.csv")
head(ddt)
```

## Task 3
- Using class() function, we can conclude that SPECIES and RIVER classes are quantitative data, since they have character values.
```{r}
class(ddt$SPECIES)
class(ddt$RIVER)
```
- Likewise, we can conclude the quantitative variables of the data frame are: MILE, LENGTH, and WEIGHT
```{r}
class(ddt$MILE)
class(ddt$LENGTH)
class(ddt$WEIGHT)
```
Next, finding observations with SPECIES, LMBASS and WEIGHT bigger than 800gms. We set species equal to "LMBASS" and WEIGHT>800.
```{r}
with(ddt, ddt[WEIGHT>800 & SPECIES=="LMBASS",])
```

Next, finding observations where the RIVER is SCM and DDT bigger than 4.0. We set RIVER equal to "SCM" and DDT>4.0.
```{r}
#FIXME
with(ddt, ddt[RIVER=="SCM" & DDT>4.0,])
```

## Task 4
The mean of length of fish:
```{r}
mean(ddt$LENGTH)
```
Finding the standard deviation of weight.
```{r}
sd(ddt$WEIGHT)
```
Verifying length vs weight
```{r}
plot(ddt$LENGTH, ddt$WEIGHT, ylab="LENGTH", xlab="WEIGHT")
1
```
Last value of v/20:
```{r}
v=1:20
v/20
```
## Task 5
Table of rivers
```{r}
# Turning RIVERS into subtable.
rivers=with(ddt, table(RIVER))
rivers
```
Creating color coded bar plot.
```{r}
barplot(rivers, col=c("red", "orange", "green", "blue"))
```
Creating a table of rivers crossed with species of fish.
```{r}
# Rivers crossed with fish.
rcf <- with(ddt, c(RIVER, SPECIES))
```
Making a barplot with rivers crossed with species of fish.
```{r}
# Rivers crossed with fish.
fcr <- with(ddt, table(SPECIES, RIVER))
barplot(fcr)
```

## Task 6
Making pie chart of fish species.
```{r}
pdata <- with(ddt, table(SPECIES))
pie(pdata, col=1:3)
```
Making pie chart of rivers
```{r}
ridata <- with(ddt, table(RIVER))
pie(ridata, col=1:4)
```

## Task 7
Making a boxplot of the variable DDT.
```{r}
boxplot(with(ddt, table(DDT)))
```
Making a boxplot of the variable WEIGHT.
```{r}
boxplot(with(ddt, table(WEIGHT)))
```
Making a boxplot of the variable LENGTH
```{r}
boxplot(with(ddt, table(LENGTH))) 
```

## Task 8
Making a coplot of LENGTH Vs WEIGHT given RIVER
```{r}
fishcol=with(ddt,ifelse(SPECIES=="CCATFISH","Red",
                        ifelse(SPECIES=="SMBUFFALO","Blue","Green")))
rivcol=with(ddt, ifelse(RIVER=="FCM","Red",
                        ifelse(RIVER=="LCM","Blue",
                               ifelse(RIVER=="SCM","Green","Black"))))
coplot(WEIGHT~LENGTH|RIVER,data=ddt,col=fishcol)
```
Making a coplot of DDT Vs WEIGHT given SPECIES
```{r}
coplot(DDT~WEIGHT|SPECIES,data=ddt,col=fishcol)
```

## Task 9
Create first ggplot2 graph.
```{r}
library(ggplot2)
ggplot(ddt, aes(x = SPECIES, y = WEIGHT, fill = RIVER)) +
  geom_boxplot(outlier.shape = 16, outlier.color = "black") +
  scale_fill_manual(values = c("FCM" = "red", "LCM" = "orange", "SCM" = "green", "TRM" = "purple")) +
  labs(title = "Cale Bible",
       x = "SPECIES",
       y = "WEIGHT",
       fill = "RIVER") +
  theme_minimal()
```
Create ggplot2 graph.
```{r}
ggplot(ddt, aes(x = RIVER, y = LENGTH, fill = SPECIES)) +
  geom_violin() +
  scale_fill_manual(values = c("CCATFISH" = "red", "LMBASS" = "green", "SMBUFFALO" = "blue")) +
  labs(title = "Cale Bible",
       x = "SPECIES",
       y = "WEIGHT",
       fill = "RIVER") +
  theme_minimal()
```
